\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-11-18 chapters/stbf_struct.tex
Textcites

  \noindent\emph{This chapter was
  published as~\textcite{VanDenKerchove2022}.}

@@

	Methods exist to estimate an optimal shrinkage value from the data directly.
	Most notable among these are the Ledoit-Wolf procedure~\cite{Ledoit2004},
	Rao-Blackwell Ledoit-Wolf~\cite{Chen2010}, and Oracle Approximating Shrinkage~\cite{Chen2010}.
  A more recent estimation method~\cite{Tong2018} emulates a \ac{loocv} scheme expressed by the data-driven closed-form
	estimate:
	\begin{equation}
		\alpha =
		1-\frac{
      \frac{N}{N-1}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			- \frac{1}{N(N-1)}\sum_{n=1}^N||\mat{x}_n||_2^4
		}
		{
      \frac{N^2 -2N}{(N-1)^2}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			+ \frac{1}{N(N-1)^2}\sum_{n=1}^N||\mat{x}_n||_2^4
		}
		\label{eq:loocv}
	\end{equation}
	We opt for the \ac{loocv} shrinkage estimator because it avoids some of the
	assumptions made by~\cite{Ledoit2004} and~\cite{Chen2010} and
	because it generalizes to structured covariance estimation as described in
	\cref{sec:stbf-struct/methods/structured-estimation}.

@@

	The \ac{eeg} recorded at 2048Hz was re-referenced off-line to the average of the mastoids.
	The reference electrodes were dropped from the analysis.
	Data were subsequently filtered between 0.5Hz and 16Hz using forward-backward
	filtering with a fourth-order Butterworth IIR filter.
	The \ac{eeg} signal was corrected for ocular artifacts using Independent Component
	Analysis (ICA) by rejecting components that correlated with the bipolar EOG
  channels vEOG and hEOG using iterative Z-score thresholding.
  Components with a Z-scored pearson correlation coefficient
  exceeding the other 3 times the standard deviation of the Z-scored
  correlation coefficients of other component's Z-scored were iteratively
  rejected until none that exceed the threshold remained.
  Finally, epochs were cut from 0.1s to 0.6s after stimulus onset.
	No baseline correction was performed since this affects the temporal covariance
	of the data, violating the Toeplitz structure assumption~\cite{Bijma2003}.

@@

  \subsubsection{\Acl{stbf} classifier}
	Before calculating the \ac{stbf}, the signal was downsampled to
	32Hz or twice the low-pass frequency 16Hz, resulting in 17 time samples
	between 0.1 and 0.6s. According to the Nyquist Theorem, more samples would not
	contain more information hence the minimum temporal resolution is chosen to reduce
	the dimensionality of the covariance and improve its condition number.
	The activation pattern is the difference between the averages of epochs in response to cued targets and the averages of those in response to non-cued targets.
	We constructed three variations of the spatiotemporal beamformer:
	\ac{stbf} with empirical covariance estimation (\textsc{stbf-emp}) as in
	\cref{sec:stbf-struct/methods/emp-cov}, \ac{stbf} with
	\ac{loocv}-shrunk covariance estimation (\textsc{stbf-shrunk}) as in
	\cref{sec:stbf-struct/methods/shrunk-cov}, and \ac{stbf} with
	Kronecker-Toeplitz structured covariance estimation (\textsc{stbf-struct}) with \ac{loocv} shrinkage for
	the Kronecker factors as in \cref{sec:stbf-struct/methods/struct-cov}.

	\subsubsection{Riemannian geometry classifier}
	\label{sec:riemannian}
	We opted for a Riemannian
	geometry-based classifier to compare our results.
	The Riemannian model (\textsc{xdawn+rg}) uses the XDAWN spatial filter combined
	with Riemannian geometry in tangent space as implemented by Barachant et
	al.~\cite{Barachant2014a}.
	This classifier uses four XDAWN spatial filters and each epoch's empirical spatial covariance matrix.
	The target with the maximum score is the prediction of the cued target.
	\textsc{xdawn+rg} was trained and validated without downsampling using epochs
	at the original sample rate of 2048Hz.

@@

	\cref{fig:iterations} confirms these results for the \textsc{stbf-struct} classifier.
	Using more than one fixed-point iteration does not significantly improve the
	accuracy across the amounts of training data and the number of trials
  used for evaluation\todo{qualitative}.
	Hence, only one iteration is used for the \textsc{stbf-struct} classifier, leading to a drastic speed-up of
  the  training process.

@@

	\subsection{Classifier accuracy for limited training data}
	It is of interest to keep the calibration time before \ac{bci}
	operation as short as possible.
	We mimic this problem by training the classifier with as few training epochs as possible.
	We evaluate the performance of all classifiers for different levels of
	available training data and apply the cross-validation procedure nine times (the number of blocks in the training fold) for all subjects, keeping the
	corresponding number of blocks in the training folds and dropping the rest.
	\Cref{fig:accuracy} and \cref{fig:stbf-struct/accuracy-ap} show each classifier's
	accuracy relative to the data availability.
	We statistically compare the two newly proposed classifiers,
	\textsc{stbf-struct} and \textsc{stbf-shrunk}, for different levels of training
	data availability using a one-sided paired Wilcoxon rank-sum test with Holm correction for the multiple pairwise comparisons between classifiers.
	We performed this analysis three times: by only using the first trial of a
	block, by averaging epochs across the first two trials of a block and across
	the first five trials of a block.
	Results validated on one trial are reported in \cref{tab:stbf-struct/p-values-1}, 2-trial results
	in \cref{tab:stbf-struct/p-values-2}, and 5-trial results in \cref{tab:stbf-struct/p-values-5}.

@@

	The tables show that \textsc{stbf-struct} has a significant advantage over
	\textsc{stbf-shrunk} when the number of training blocks is low.
  This effect is present for 1-, 2- and 5-trial evaluation\todo{qualitative}.
	This advantage decreases (the $p$-value increases) when
  adding more training blocks\todo{qualitative}.
	Both \textsc{stbf-struct} and \textsc{stbf-shrunk} perform significantly better
  than \textsc{stbf-emp} for all evaluated settings\todo{qualitative}.
	Compared to \textsc{xdawn+rg}, \textsc{stbf-struct} also has significantly
	higher accuracy in almost all evaluated settings, except when using only one
  training block\todo{qualitative}.
	\textsc{stbf-shrunk} does not outperform \textsc{xdawn+rg} when training data
  is low but gains a significant advantage	when using more training
  data\todo{qualitative}.

@@

	\Cref{fig:stbf-struct/training-time} shows that the training time of
	\textsc{stbf-struct} has a lower median training time than
  \textsc{stbf-shrunk}, \textsc{stbf-emp} and \textsc{xdawn+rg} when training
  on all available data and using 32 channels\todo{qualitative}.

@@

	\subsection{Classification accuracy}
	As evidenced by \cref{fig:accuracy} and Tables \ref{tab:stbf-struct/p-values-1}-\ref{tab:stbf-struct/p-values-5}, the regularized classifiers \textsc{stbf-shrunk}
	and \textsc{stbf-struct} significantly improve the classification accuracy
	compared to the original \textsc{stbf-emp} for all numbers of training blocks
  indicated\todo{qualitative}.
	We believe there are three reasons for this.
	First and foremost, the empirical covariance matrix in \textsc{stbf-emp} becomes
	ill-conditioned when the number of available training epochs is smaller than
	the number of features ($N<CS$), rendering its inversion with the
	Moore-Penrose pseudoinverse unstable.
	This is the case \textsc{stbf-emp} when $N=CS=32*17=544$, after which the
	accuracy of \textsc{stbf-emp} starts to increase.
	This effect is visible in \cref{fig:accuracy}, where the accuracy starts
	increasing when using more than four training blocks, amounting to 540 epochs.
	The noticeable dip in accuracy when using around 540 epochs can be explained by
	numerical effects in the pseudoinverse for very small
	eigenvalues~\cite{Blankertz2011, Raudys1998, Schaefer2004,
		Kraemer2009}.
	Regularization of the covariance matrix with shrinkage ensures that the
	covariance matrix is non-singular and better conditioned so it can stably be inverted.
	Second, covariance regularization introduces a trade-off between variance and bias of the model~\cite{Ledoit2004}.
	Better performance on unseen data can be achieved when some model variance is
	traded for extra bias.
	Regularization reduces extreme values present, as shown in
	\cref{fig:kronlda-covs}, resulting in a classifier with
	better generalization.
	Third, the true spatiotemporal covariance matrix may vary throughout \ac{bci}
	sessions, e.g., due to movement of the \ac{eeg}-cap, changing impedances of
	electrodes, subject fatigue, the introduction of new spatiotemporal noise
	sources, and other possible confounds.
	A regularized covariance matrix should better account for changes in true covariance.
	Note that the \ac{loocv} method in principle assumes that the covariances of
	the training data and unseen data are the same.
	Because the covariance might have changed for unseen data, the shrinkage
	estimate obtained with \ac{loocv} is probably still an
	underestimation of the optimal -- but unknown -- shrinkage coefficient that
	would yield the best classification accuracy for the unseen data.

	Another observation is the significantly better accuracy score of
	\textsc{stbf-struct} over \textsc{stbf-shrunk} when the amount of available
  training data is small\todo{qualitative}.
	This property is an attractive advantage in a \ac{bci} setting since it is desirable to keep the calibration (training) phase as short as possible without losing accuracy.
	The accuracy advantage of the structured estimator is a consequence of the
	Kronecker-Toeplitz covariance structure, which is informative for the
	underlying process generating the epochs, if it is assumed that the \ac{eeg} signal
	is a linear combination of stationary activity generated by random dipoles in
	the brain with added noise~\cite{Munck1992, DeMunck2002, GonzalezNavarro2017}.
	Hence, \textsc{stbf-struct} can utilize this prior information to better estimate the inverse
	covariance.
  The increase in accuracy for small training set sizes\todo{qualitative} can also be explained by the smaller number of parameters necessary to estimate the inverse covariance (see \cref{sec:stbf-struct/discussion/param-complex}), increasing the stability of matrix inversions.

	When compared to the state-of-the-art \textsc{xdawn+rg} classifier, we conclude
	that \textsc{stbf-struct} reaches similar accuracy when using only one block of
  training data\todo{qualitative}.
	The authors suspect this is due to both
	classifiers having insufficient training information to reach
	satisfactory classification accuracy.
	When more data are available, \textsc{stbf-struct} reaches significantly
  better accuracies\todo{qualitative}.
	Combined with the benefits laid out in \cref{sec:stbf-struct/discussion/param-complex}, this
  makes it an attractive option for \ac{erp} classification.
	\textsc{stbf-shrunk} does not show decisive accuracy improvements over
	\textsc{xdawn+rg} using a few training blocks, but this improves as the
  training data increases\todo{qualitative}.

@@

	Second, structured estimation has better time complexity.
	Covariance estimation and inversion occupy the largest part of the \ac{stbf} training time.
	For \textsc{stbf-emp} and \textsc{stbf-shrunk}, the time complexity of this process is $\mathcal{O}(NC^2S^2+C^3S^3)$.
	Thanks to Property~\ref{prop:stbf-struct/inverse-kronecker}, the complexity can be reduced to
	$\mathcal{O}(NS^2S^2+C^3+S^3)$ for the structured estimator of \textsc{stbf-struct}.
	The results presented in \cref{fig:stbf-struct/training-time} confirm these
	calculations.
	It can be observed that the training time of \textsc{stbf-struct} stays low
  compared to \textsc{stbf-emp} and \textsc{stbf-shrunk} when dimensionality
  increases\todo{qualitative}.

@@

	\section{Conclusion}
	While it is possible to regularize the spatiotemporal \ac{lcmv} beamformer
	classifier for \ac{erp} detection with other methods such as by employing feature selection,
	by adding regularizing penalties to the cost
	function beamforming problem, or by crafting a cleaner activation pattern, our work focused on
	estimation methods for the spatiotemporal covariance.
	We introduced a covariance estimator using adaptive shrinkage and an
	estimator exploiting prior knowledge about the spatiotemporal nature of the \ac{eeg}
	signal.
	We compared these estimators with the original spatiotemporal
	beamformer and a state-of-the-art method in an off-line P3 detection task.
	Our results show that the structured estimator performs better when training
  data are sparsely available and that it can be computed faster and with
  substantially less memory usage\todo{qualitative}.
	Since these algorithms are not paradigm-specific,  the conclusions can be generalized to
	other \ac{erp}-based \ac{bci} settings.

@@

  \footnotesize
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-stbf_kron_toep_shrunk.tex}
      \caption{Accuracies for \textsc{stbf-struct}.}
  \end{table}
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-stbf_loocv.tex}
      \caption{Accuracies for \textsc{stbf-shrunk}.}
  \end{table}
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-stbf_emp.tex}
      \caption{Accuracies for \textsc{stbf-emp}.}
  \end{table}
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-xdawn_rg.tex}
      \caption{Accuracies for \textsc{xdawn+rg}.}
  \end{table}

@@

  \clearpage
  \section{Statistical comparisons}
  \begin{table}[h]
    \footnotesize
    \begin{subtable}{\linewidth}
	    \input{chapters/stbf_struct_tests_1.tex}
	    \caption{Evaluation on one testing trial.}
      \label{tab:stbf-struct/p-values-1}
    \end{subtable}
    \bigskip

    \begin{subtable}{\linewidth}
	    \input{chapters/stbf_struct_tests_2.tex}
	    \caption{Evaluation averaging over two testing trials.}
	    \label{tab:stbf-struct/p-values-2}
    \end{subtable}
    \bigskip

    \begin{subtable}{\linewidth}
	    \input{chapters/stbf_struct_tests_3.tex}
	    \caption{Evaluation averaging over five testing trials.}
	    \label{tab:stbf-struct/p-values-5}
    \end{subtable}
    \caption[Statistical significance of differences in classifier
    performance.]{%
        Statistical significance of differences in classifier performance.
        $p$-values calculated by one-sided paired Wilcoxon rank-sum test with
	    	Holm correction using one testing trial for different classifiers
	    	and levels of data availability. $p$-values $<0.05$ are considered
        significant.
    }
	\end{table}

>>>>

  \noindent\emph{This chapter, except
  \crefrange{tab:stbf-struct/accuracies/stbf-struct}{tab:stbf-struct/accuracies/xdawn-rg},
  was published as~\textcite{VanDenKerchove2022}.}

@@

	Methods exist to estimate an optimal shrinkage value from the data directly.
	Most notable among these are the Ledoit-Wolf procedure~\cite{Ledoit2004},
	Rao-Blackwell Ledoit-Wolf~\cite{Chen2010}, and Oracle Approximating Shrinkage~\cite{Chen2010}.
  A more recent estimation method~\cite{Tong2018} emulates a \ac{loocv} scheme expressed by the data-driven closed-form
	estimate:
	\begin{equation}
		\alpha =
		1-\frac{
      \frac{N}{N-1}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			- \frac{1}{N(N-1)}\sum_{n=1}^N||\mat{x}_n||_2^4
		}
		{
      \frac{N^2 -2N}{(N-1)^2}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
      - \frac{2}{CS}\left[\text{Tr}(\hat{\mat{C}}_\text{emp})\right]^2
      + \frac{1}{CS}\text{Tr}(\hat{\mat{C}}_\text{emp}^2)
			+ \frac{1}{N(N-1)^2}\sum_{n=1}^N||\mat{x}_n||_2^4
		}
		\label{eq:loocv}
	\end{equation}
	We opt for the \ac{loocv} shrinkage estimator because it avoids some of the
	assumptions made by \textcite{Ledoit2004} and \textcite{Chen2010} and
	because it generalizes to structured covariance estimation as described in
	\cref{sec:stbf-struct/methods/structured-estimation}.

@@

	The \ac{eeg} recorded at 2048 Hz was re-referenced off-line to the average of the mastoids.
	The reference electrodes were dropped from the analysis.
	Data were subsequently filtered between 0.5 Hz and 16 Hz using forward-backward
	filtering with a fourth-order Butterworth IIR filter.
	The \ac{eeg} signal was corrected for ocular artifacts using Independent Component
	Analysis (ICA) by rejecting components that correlated with the bipolar EOG
  channels vEOG and hEOG using iterative Z-score thresholding.
  Components with a Z-scored pearson correlation coefficient
  exceeding the other 3 times the standard deviation of the Z-scored
  correlation coefficients of other component's Z-scored were iteratively
  rejected until none that exceed the threshold remained.
  Finally, epochs were cut from 0.1s to 0.6s after stimulus onset.
	No baseline correction was performed since this affects the temporal covariance
	of the data, violating the Toeplitz structure assumption~\cite{Bijma2003}.

@@

  \subsubsection{\Acl{stbf} classifier}
	Before calculating the \ac{stbf}, the signal was downsampled to
	32 Hz or twice the low-pass frequency 16 Hz, resulting in 17 time samples
	between 0.1 and 0.6s. According to the Nyquist Theorem, more samples would not
	contain more information hence the minimum temporal resolution is chosen to reduce
	the dimensionality of the covariance and improve its condition number.
	The activation pattern is the difference between the averages of epochs in response to cued targets and the averages of those in response to non-cued targets.
	We constructed three variations of the spatiotemporal beamformer:
	\ac{stbf} with empirical covariance estimation (\textsc{stbf-emp}) as in
	\cref{sec:stbf-struct/methods/emp-cov}, \ac{stbf} with
	\ac{loocv}-shrunk covariance estimation (\textsc{stbf-shrunk}) as in
	\cref{sec:stbf-struct/methods/shrunk-cov}, and \ac{stbf} with
	Kronecker-Toeplitz structured covariance estimation (\textsc{stbf-struct}) with \ac{loocv} shrinkage for
	the Kronecker factors as in \cref{sec:stbf-struct/methods/struct-cov}.

	\subsubsection{Riemannian geometry classifier}
	\label{sec:riemannian}
	We opted for a Riemannian
	geometry-based classifier to compare our results.
	The Riemannian model (\textsc{xdawn+rg}) uses the XDAWN spatial filter combined
	with Riemannian geometry in tangent space as implemented by Barachant et
	al.~\cite{Barachant2014a}.
	This classifier uses four XDAWN spatial filters and each epoch's empirical spatial covariance matrix.
	The target with the maximum score is the prediction of the cued target.
	\textsc{xdawn+rg} was trained and validated without downsampling using epochs
	at the original sample rate of 2048 Hz.

@@

	\cref{fig:iterations} confirms these results for the \textsc{stbf-struct} classifier.
	Using more than one fixed-point iteration does not significantly improve the
	accuracy across the amounts of training data and the number of trials
  used for evaluation.
	Hence, only one iteration is used for the \textsc{stbf-struct} classifier, leading to a drastic speed-up of
  the  training process.

@@

	\subsection{Classifier accuracy for limited training data}
	It is of interest to keep the calibration time before \ac{bci}
	operation as short as possible.
	We mimic this problem by training the classifier with as few training epochs as possible.
	We evaluate the performance of all classifiers for different levels of
	available training data and apply the cross-validation procedure nine times (the number of blocks in the training fold) for all subjects, keeping the
	corresponding number of blocks in the training folds and dropping the rest.
  \Cref{fig:accuracy}, \cref{fig:stbf-struct/accuracy-ap} and
  \crefrange{tab:stbf-struct/accuracy/stbf-struct}{tab:stbf-struct/accuracy/xdawn-rg}
  shows each classifier's accuracy relative to the data availability and trials
  used for agveraging.
	We statistically compare the two newly proposed classifiers,
	\textsc{stbf-struct} and \textsc{stbf-shrunk} with different levels of training
	data availability using a one-sided paired Wilcoxon rank-sum test with Holm correction for the multiple pairwise comparisons between classifiers.
	Statistical comparisons were performed for trial
  \cref{tab:stbf-struct/p-values-1}, two \cref{tab:stbf-struct/p-values-2}
  and five trials \cref{tab:stbf-struct/p-values-5}.

@@

	The tables show that \textsc{stbf-struct} has a significant advantage over
  \textsc{stbf-shrunk} when the number of training blocks is low, with
  significance $p=0.005$ and  an accuracy increase of 4,14$\%.$ for a single training block
  and testing trial.
  This effect is present for 1-, 2- and 5-trial evaluation, up to 3, 4 and 3
  blocks respectively, but the advantage decreases when adding more training blocks.
	Both \textsc{stbf-struct} and \textsc{stbf-shrunk} perform significantly better
  than \textsc{stbf-emp} for all evaluated settings, with $p<0.001$ for all number
  of training blocks and testing trials, with accuracy
  increase of 6.92 and 2.78$\%.$ respectively for a single training block
  and testing trial.
	Compared to \textsc{xdawn+rg}, \textsc{stbf-struct} also has significantly
	higher accuracy in almost all evaluated settings, except when using only one
  training block, with significance $p<0.001$ and an accuracy increase of
  5.20$\%.$ when using all 9 training blocks and 1 testing trial.
	\textsc{stbf-shrunk} does not outperform \textsc{xdawn+rg} when training data
  is low (up to 3,3 and 2 blocks respectively for 1, 2 and 5 testing trials),
  but gains a significant advantage	when using more training data, with
  significange $p=0.001$ and an accuracy increase of 5.33$\%.$ when using all
  9 training blocks and 1 testing trial.

@@

	\Cref{fig:stbf-struct/training-time} shows that the training time of
  \textsc{stbf-struct} has a lower median training time (0.06 s) than
  \textsc{stbf-shrunk} (0.33 s), \textsc{stbf-emp} (0.30 s) and
  \textsc{xdawn+rg} (1.04 s) when training
  on all available data and using 32 channels.

@@

	\subsection{Classification accuracy}
	As evidenced by \cref{fig:accuracy} and \cref{tab:stbf-struct/p-values},
  the regularized classifiers \textsc{stbf-shrunk}
	and \textsc{stbf-struct} significantly improve the classification accuracy
	compared to the original \textsc{stbf-emp} for all numbers of training blocks
  indicated.
	We believe there are three reasons for this.
	First and foremost, the empirical covariance matrix in \textsc{stbf-emp} becomes
	ill-conditioned when the number of available training epochs is smaller than
	the number of features ($N<CS$), rendering its inversion with the
	Moore-Penrose pseudoinverse unstable.
	This is the case \textsc{stbf-emp} when $N=CS=32*17=544$, after which the
	accuracy of \textsc{stbf-emp} starts to increase.
	This effect is visible in \cref{fig:accuracy}, where the accuracy starts
	increasing when using more than four training blocks, amounting to 540 epochs.
	The noticeable dip in accuracy when using around 540 epochs can be explained by
	numerical effects in the pseudoinverse for very small
	eigenvalues~\cite{Blankertz2011, Raudys1998, Schaefer2004,
		Kraemer2009}.
	Regularization of the covariance matrix with shrinkage ensures that the
	covariance matrix is non-singular and better conditioned so it can stably be inverted.
	Second, covariance regularization introduces a trade-off between variance and bias of the model~\cite{Ledoit2004}.
	Better performance on unseen data can be achieved when some model variance is
	traded for extra bias.
	Regularization reduces extreme values present, as shown in
	\cref{fig:kronlda-covs}, resulting in a classifier with
	better generalization.
	Third, the true spatiotemporal covariance matrix may vary throughout \ac{bci}
	sessions, e.g., due to movement of the \ac{eeg}-cap, changing impedances of
	electrodes, subject fatigue, the introduction of new spatiotemporal noise
	sources, and other possible confounds.
	A regularized covariance matrix should better account for changes in true covariance.
	Note that the \ac{loocv} method in principle assumes that the covariances of
	the training data and unseen data are the same.
	Because the covariance might have changed for unseen data, the shrinkage
	estimate obtained with \ac{loocv} is probably still an
	underestimation of the optimal -- but unknown -- shrinkage coefficient that
	would yield the best classification accuracy for the unseen data.

	Another observation is the significantly better accuracy score of
	\textsc{stbf-struct} over \textsc{stbf-shrunk} when the amount of available
  training data is small ($<540$ epochs).
	This property is an attractive advantage in a \ac{bci} setting since it is desirable to keep the calibration (training) phase as short as possible without losing accuracy.
	The accuracy advantage of the structured estimator is a consequence of the
	Kronecker-Toeplitz covariance structure, which is informative for the
	underlying process generating the epochs, if it is assumed that the \ac{eeg} signal
	is a linear combination of stationary activity generated by random dipoles in
	the brain with added noise~\cite{Munck1992, DeMunck2002, GonzalezNavarro2017}.
	Hence, \textsc{stbf-struct} can utilize this prior information to better estimate the inverse
	covariance.
  The increase in accuracy for small training set sizes can also be explained by the smaller number of parameters necessary to estimate the inverse covariance (see \cref{sec:stbf-struct/discussion/param-complex}), increasing the stability of matrix inversions.

	When compared to the state-of-the-art \textsc{xdawn+rg} classifier, we conclude
	that \textsc{stbf-struct} reaches similar accuracy when using only one block of
  training data, with accuracies of and 34.70\% 32.5\% respectively and $p=0.086$.
	The authors suspect this is due to both	classifiers having insufficient training
  information to reach satisfactory classification accuracy.
	When more data are available, \textsc{stbf-struct} reaches significantly
  better accuracies.
	Combined with the benefits laid out in \cref{sec:stbf-struct/discussion/param-complex}, this
  makes it an attractive option for \ac{erp} classification.
	\textsc{stbf-shrunk} does not show decisive accuracy improvements over
	\textsc{xdawn+rg} using a few training blocks, but this improves as the
  training data increases.

@@

	Second, structured estimation has better time complexity.
	Covariance estimation and inversion occupy the largest part of the \ac{stbf} training time.
	For \textsc{stbf-emp} and \textsc{stbf-shrunk}, the time complexity of this process is $\mathcal{O}(NC^2S^2+C^3S^3)$.
	Thanks to Property~\ref{prop:stbf-struct/inverse-kronecker}, the complexity can be reduced to
	$\mathcal{O}(NS^2S^2+C^3+S^3)$ for the structured estimator of \textsc{stbf-struct}.
	The results presented in \cref{fig:stbf-struct/training-time} confirm that
  \textsc{stbf-struct} is much faster in operation than other classifiers.

@@

	\section{Conclusion}
	While it is possible to regularize the spatiotemporal \ac{lcmv} beamformer
	classifier for \ac{erp} detection with other methods such as by employing feature selection,
	by adding regularizing penalties to the cost
	function beamforming problem, or by crafting a cleaner activation pattern, our work focused on
	estimation methods for the spatiotemporal covariance.
	We introduced a covariance estimator using adaptive shrinkage and an
	estimator exploiting prior knowledge about the spatiotemporal nature of the \ac{eeg}
	signal.
	We compared these estimators with the original spatiotemporal
	beamformer and a state-of-the-art method in an off-line P3 detection task.
	Our results show that the structured estimator performs better when training
  data are sparsely available and that it can be computed faster and with
  substantially less memory usage.
	Since these algorithms are not paradigm-specific,  the conclusions can be generalized to
	other \ac{erp}-based \ac{bci} settings.

@@

  \footnotesize
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-stbf_kron_toep_shrunk.tex}
      \caption[Accuracies for \textsc{stbf-struct}.]{Accuracies (\%) for \textsc{stbf-struct}.}
      \label{tab:stbf-struct/accuracies/stbf-struct}
  \end{table}
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-stbf_loocv.tex}
      \caption[Accuracies for \textsc{stbf-struct}.]{Accuracies (\%) for
      \textsc{stbf-shrunk}.}
      \label{tab:stbf-struct/accuracies/stbf-shrunk}
  \end{table}
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-stbf_emp.tex}
      \caption[Accuracies for \textsc{stbf-struct}.]{Accuracies (\%) for
      \textsc{stbf-emp}.}
      \label{tab:stbf-struct/accuracies/stbf-emp}
  \end{table}
  \begin{table}[!h]
	    \input{chapters/stbf_struct-acc-xdawn_rg.tex}
      \caption[Accuracies for \textsc{stbf-struct}.]{Accuracies (\%) for
      \textsc{xdawn+rg}.}
      \label{tab:stbf-struct/accuracies/xdawn-rg}
  \end{table}

@@

  \clearpage
  \section{Statistical comparisons}
  \begin{table}[h]
    \footnotesize
    \begin{subtable}{\linewidth}
	    \input{chapters/stbf_struct_tests_1.tex}
	    \caption{Evaluation on one testing trial.}
      \label{tab:stbf-struct/p-values-1}
    \end{subtable}
    \smallskip

    \begin{subtable}{\linewidth}
	    \input{chapters/stbf_struct_tests_2.tex}
	    \caption{Evaluation averaging over two testing trials.}
	    \label{tab:stbf-struct/p-values-2}
    \end{subtable}
    \smallskip

    \begin{subtable}{\linewidth}
	    \input{chapters/stbf_struct_tests_3.tex}
	    \caption{Evaluation averaging over five testing trials.}
	    \label{tab:stbf-struct/p-values-5}
    \end{subtable}
    \caption[Statistical significance of differences in classifier
    performance.]{%
        Statistical significance of differences in classifier performance.
        $p$-values calculated by one-sided paired Wilcoxon rank-sum test with
	    	Holm correction using one testing trial for different classifiers
	    	and levels of data availability. $p$-values $<0.05$ are considered
        significant.
    }
	  \label{tab:stbf-struct/p-values}
	\end{table}
